---
title: "coralcolours taxonomy"
format:
  html:
    code-fold: true
    code-show: false
editor: visual
execute:
  echo: false
---

#### `acanthastrea`

^*Acanthastrea echinata*^

```{r}
#| fig-width: 14
#| fig-height: 2
#| message: false
#| warning: false
library(coralcolors)

acanthastrea <- c("#2D4F68", "#0570C2","#039FFF","#018CAF","#00B09C", "#F9B908", "#A84743")
show_colors(acanthastrea, nrow=1)
```

#### `acropora1`

^*Acropora cervicornis*^

```{r}
#| fig-width: 14
#| fig-height: 2

acropora1 <-c("#453e1e", "#97976f", "#c3cab3", "#5b8b7d", "#28607b", "#275d6a")
show_colors(acropora1, nrow=1)
```

#### `acropora2`

^*Acropora palmata*^

```{r}
#| fig-width: 14
#| fig-height: 2

acropora2 <-c( "#908A7B", "#dbd798", "#90C3D0", "#fdde2e", "#f5b11e", "#c98230")
show_colors(acropora2, nrow=1)
```

#### `acropora3`

^*Acropora millepora*^

```{r}
#| fig-width: 14
#| fig-height: 2

acropora3 <-c( "#0b043e", "#6a5478", "#a9727a", "#82a0d2", "#ffcaa4", "#b65039")
show_colors(acropora3, nrow=1)
```

#### `acropora4`

^*Acropora tenuis*^

```{r}
#| fig-width: 14
#| fig-height: 2

tenuis <-c( "#deb9ff", "#cf69e4", "#6a27b7", "#572180", "#420868", "#28083e")
show_colors(acropora4, nrow=1)
```

#### `australophyllia`

^*Australophyllia wilsonii*^

```{r}
#| fig-width: 14
#| fig-height: 2
#| message: false
#| warning: false

australophyllia <- c("#5e263c", "#b14a45", "#da867a","#b6cdad","#5d8357","#5483bb", "#2a52ce")
show_colors(australophyllia, nrow=1)
```

#### `cyphastrea`

^*Cyphastrea sp.*^

```{r}
#| fig-width: 14
#| fig-height: 2

cyphastrea <- c("#8e4c2d", "#d26e38", "#f0ac22", "#5561aa", "#3652a1", "#252962", "#171025")
show_colors(cyphastrea, nrow=1)

```

#### `montipora`

^*Montipora digitata*^

```{r}
#| fig-width: 14
#| fig-height: 2
#| message: false
#| warning: false

montipora <- c("#a67fac", "#4c5383","#8d98cc", "#929e46", "#c3d4c2","#d15753", "#b0322f")
show_colors(montipora, nrow=1)
```

#### `micromussa`

^*Micromussa\ lordhowensis*^

```{r}
#| fig-width: 14
#| fig-height: 2

micromussa <- c("#3C82F3", "#FF6F68", "#A86D9D", "#77A7CD", "#643995", "#46588F", "#5960EC")
show_colors(micromussa, nrow=1)

```

#### `porites`

^*Porites lobata*^

```{r}
#| fig-width: 14
#| fig-height: 2

porites <- c("#422b35", "#815850", "#c78f7d",  "#cdbaae", "#627886", "#5f999f", "#384b74")

show_colors(porites, nrow=1)
```

#### `seriatopora`

^*Seriatopora hysterix*^

```{r}
#| fig-width: 14
#| fig-height: 2

seriatopora <- c("#e1cbe0", "#c797c5" ,"#b377b3", "#a65497", "#943e70", "#6f293d", "#34111a")
show_colors(seriatopora, nrow=1)
```

#### `symbiodinium`

^*Symbiodinium sp.*^

```{r}
#| fig-width: 14
#| fig-height: 2
#| message: false
#| warning: false

symbiodinium <- c("#6e4c1f","#9e743a","#a29070","#a9a89f", "#acbdc2", "#beced6")
show_colors(symbiodinium, nrow=1)
```
