---
title: "coralcolours bleaching"
format:
  html:
    code-fold: false
    code-show: true
editor: visual
---

#### `acanthastrea`

^*Acanthastrea echinata*^

```{r}
#| fig-width: 14
#| fig-height: 2
#| message: false
#| warning: false

library(coralcolors)
show_colors(coral_palettes$acanthastrea, nrow=1)
show_colors(bleach(coral_palettes$acanthastrea), nrow=1)
```

#### `acropora1`

^*Acropora cervicornis*^

```{r}
#| fig-width: 14
#| fig-height: 2

show_colors(coral_palettes$acropora1, nrow=1)
show_colors(bleach(coral_palettes$acropora1), nrow=1)
```

#### `acropora2`

^*Acropora palmata*^

```{r}
#| fig-width: 14
#| fig-height: 2

show_colors(coral_palettes$acropora2, nrow=1)
show_colors(bleach(coral_palettes$acropora2), nrow=1)
```

#### `acropora3`

^*Acropora millepora*^

```{r}
#| fig-width: 14
#| fig-height: 2

show_colors(coral_palettes$acropora3, nrow=1)
show_colors(bleach(coral_palettes$acropora3), nrow=1)
```

#### `acropora4`

^*Acropora tenuis*^

```{r}
#| fig-width: 14
#| fig-height: 2

show_colors(coral_palettes$acropora4, nrow=1)
show_colors(bleach(coral_palettes$acropora4), nrow=1)

```

#### `australophyllia`

^*Australophyllia wilsonii*^

```{r}
#| fig-width: 14
#| fig-height: 2
#| message: false
#| warning: false

show_colors(coral_palettes$australophyllia, nrow=1)
show_colors(bleach(coral_palettes$australophyllia), nrow=1)
```

#### `cyphastrea`

^*Cyphastrea sp.*^

```{r}
#| fig-width: 14
#| fig-height: 2

show_colors(coral_palettes$cyphastrea, nrow=1)
show_colors(bleach(coral_palettes$cyphastrea), nrow=1)
```

#### `montipora`

^*Montipora digitata*^

```{r}
#| fig-width: 14
#| fig-height: 2
#| message: false
#| warning: false

show_colors(coral_palettes$montipora, nrow=1)
show_colors(bleach(coral_palettes$montipora), nrow=1)
```

#### `micromussa`

^*Micromussa lordhowensis*^

```{r}
#| fig-width: 14
#| fig-height: 2

show_colors(coral_palettes$micromussa, nrow=1)
show_colors(bleach(coral_palettes$micromussa), nrow=1)

```

#### `porites`

^*Porites lobata*^

```{r}
#| fig-width: 14
#| fig-height: 2

show_colors(coral_palettes$porites, nrow=1)
show_colors(bleach(coral_palettes$porites), nrow=1)
```

#### `seriatopora`

^*Seriatopora hysterix*^

```{r}
#| fig-width: 14
#| fig-height: 2

show_colors(coral_palettes$seriatopora, nrow=1)
show_colors(bleach(coral_palettes$seriatopora), nrow=1)
```

#### `symbiodinium`

^*Symbiodinium sp.*^

```{r}
#| fig-width: 14
#| fig-height: 2
#| message: false
#| warning: false

show_colors(coral_palettes$symbiodinium, nrow=1)
show_colors(bleach(coral_palettes$symbiodinium), nrow=1)
```
